\Huge \bf \sc Calibration of an inertial measurement unit

### 2013-07-30 latex/paper_sensores/paper.tex
ahora si terminado

\begin{figure}[h]
	\centering
	\includegraphics[width=.6\columnwidth]{./pics_paper/mongoose.png}
	\caption{\textbf{Mongoose -} Inertial Measurement Unit used. Red arrows represent the axis platform $S - \{\hat{i}, \hat{j}, \hat{k} \}$. }
	\label{fig:mongoose}
\end{figure}

@@

In this work we also propose to implement a temperature adjustment. The sensors are exposed to the operating temperature of the system, and it is very common that this temperature is different from the calibration temperature. The thermometer used in this work is the internal thermometer of the IMU, which indicates very precisely the operating temperature of the sensor. Sensors based in MEMS technology are sensitive to such variations. The variation of the measures is critical in some applications (see \cite{bib:uquad} for example). In INS two of the Euler angles are usually obtained from the accelerometer, therefore if the measures are not certain the stability of the system cannot be guaranteed.\\

@@

The mean error obtained correspond to less that a bit of error and the standard deviation to a bit and a half. Therefore we can conlude that a very good calibration has been achived for the static parameters of the accelerometer.\\

>>>>

\begin{figure}[h]
	\centering
	\includegraphics[width=.6\columnwidth]{./pics_paper/mongoose.png}
	\caption{\textbf{Mongoose -} Inertial Measurement Unit used. Black arrows represent the axis platform $S - \{\hat{i}, \hat{j}, \hat{k} \}$. }
	\label{fig:mongoose}
\end{figure}

@@

In this work we also propose to implement a temperature adjustment. The sensors are exposed to the operating temperature of the system, and it is very common that this temperature is different from the calibration temperature. The thermometer used in this work is the internal thermometer of the IMU, which indicates very precisely the operating temperature of the sensor. Sensors based in MEMS technology are sensitive to such variations. The variation of the measures is critical in some applications. In INS two of the Euler angles are usually obtained from the accelerometer, therefore if the measures are not certain the stability of the system cannot be guaranteed.\\

@@

The mean error obtained correspond to less that a bit of error and the standard deviation to a bit and a half. Therefore we can conlude that a very good calibration has been achieved for the static parameters of the accelerometer.\\
